### 2016-08-25 Results/TurkExp1WriteUp.Rnw
proportion test - certainty and correctness

Next, we investigate the confidence of the experiment's participants in selecting the most different plot from the others. Overall, in 40\% of the responses, the respondent was certain they were correct. User confidence in the remaining categories, neutral, uncertain, very certain, and very uncertain, was 26.88\%, 16.88\%, 9.48\%, and 6.76\%, respectively. These results are summarized by lineup in Figure~\ref{fig:cert_plot}.

@@

prop.table(table(res2$conf_level, res2$correct))

@

@@

<<time_plot, echo=FALSE>>=
#qplot(x = res2$time, binwidth = 2)
#ggplot(data = res2, aes(x = conf_level, y = time)) + geom_boxplot() + coord_flip()
ggplot(data = res2, aes(x = lineup_name, y = time)) + 
  geom_boxplot() + 
#  facet_wrap(~conf_level) + 
  coord_flip() + 
  theme_bw() + 
  labs(x = "Time (in seconds)", y = "Lineup Name")
@

>>>>

Next, we investigate the confidence of the experiment's participants in selecting the most different plot from the others. Overall, in 40\% of the responses, the respondent was certain they were correct. User confidence in the remaining categories, neutral, uncertain, very certain, and very uncertain, was 26.88\%, 16.88\%, 9.48\%, and 6.76\%, respectively. These results are summarized by lineup in Figure~\ref{fig:cert_plot}. We also performed a 5-sample test for equality of proportions in order to test the null hypothesis that the proportion of correct responses is the same in all 5 certainty categories. This test resulted in a $p$-value of 0.5881, so there is no evidence that the certainty of a user's response affects whether or not they choose the correct plot. This provides further evidence that detecting a network simulated from a different model is an extremely difficult problem.

@@

summary.conf <- data.frame(table(res2$conf_level, res2$correct))
summary.conf %>% tidyr::spread(Var2, Freq) -> summary.conf
rownames(summary.conf) <- as.character(summary.conf[,1])
names(summary.conf) <- c("Var1", "Failures", "Successes")
summary.conf <- summary.conf[,-1]
summary.conf <- summary.conf[,c(2,1)]
prop_test_for_conf_corr <- prop.test(as.matrix(summary.conf))
@

@@

<<time_plot, echo=FALSE>>=
#qplot(x = res2$time, binwidth = 2)
ggplot(data = res2, aes(x = conf_level, y = time)) + geom_boxplot() + coord_flip()
ggplot(data = res2, aes(x = lineup_name, y = time)) + 
  geom_boxplot() + 
#  facet_wrap(~conf_level) + 
  coord_flip() + 
  theme_bw() + 
  labs(x = "Time (in seconds)", y = "Lineup Name")
@
